SMT-Based Context-Bounded Model Checking for Embedded Systems: State of the Art and Future Trends

### 2016-03-20 paper.tex
review ACHIEVEMENTS

\textbf{(RP4)} State of the art SMT-based context-BMC approaches were extended to verify overflow, limit cycle, time constraints, stability, and minimum phase, in digital filters and controllers~\cite{dsv_spin2015,esbmc_controller,esbmc_filter}, and to specify system-level properties using linear-time temporal logic~\cite{JMorse15}. In particular, a specific UAV application was tackled, with the goal to verify its attitude controllers~\cite{Bessa16}. In general, however, there is still a lack of studies to verify system-level properties related to embedded systems; in particular, micro-grids~\cite{xu15} and cyber-physical systems~\cite{leeCPS2}, which require high-dependability requirements for computation, control, and communication.

Lastly, yet importantly, BMC tools like CBMC~\cite{Clarke04}, ESBMC~\cite{MorseCNF13,MorseRCN014}, and LLBMC~\cite{MerzFS12} represent the most prominent ones for verifying C programs, as observed in the Intl. Competition on Software Verification~\cite{Beyer14,BeyerSVCOMP15}.

@@

%47
\bibitem{KahlonWG09}
Kahlon V, Wang C, Gupta A.
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order
  Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

>>>>

\textbf{(RP4)} State of the art SMT-based context-BMC approaches were extended to verify overflow, limit cycle, time constraints, stability, and minimum phase, in digital systems; in particular, digital filters and controllers~\cite{dsv_spin2015,esbmc_controller,esbmc_filter}, and to specify system-level properties of those systems using linear-time temporal logic~\cite{JMorse15}. In particular, a specific UAV application was tackled, with the goal to verify its attitude controllers~\cite{Bessa16}. In general, however, there is still a lack of studies to verify system-level properties related to embedded systems; emphasis should be given to micro-grids~\cite{xu15} and cyber-physical systems~\cite{leeCPS2}, which require high-dependability requirements for computation, control, and communication. Additionally, the application of automated fault detection, localization, and correction techniques to digital systems represents an important research direction to make BMC tools useful for engineers~\cite{Alves15}.

Lastly, yet importantly, BMC tools like CBMC~\cite{Clarke04}, ESBMC~\cite{MorseCNF13,MorseRCN014}, and LLBMC~\cite{MerzFS12} represent the most prominent ones for verifying C programs, as observed in the Intl. Competition on Software Verification~\cite{Beyer14,BeyerSVCOMP15}, where verifiable (correctness and violation) witnesses are of extreme importance for evaluating software verifiers~\cite{BeyerW15,RochaIFM12}.

@@

%47
\bibitem{KahlonWG09}
Kahlon V., Wang C., Gupta A.:
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

%48
\bibitem{Alves15}
Alves E. , Cordeiro L., Lima Filho E.:
\newblock {\em{ Fault Localization in Multi-Threaded C Programs using Bounded Model Checking}}. 
\newblock In: Brazilian Symposium on Computing Systems Engineering, pp. 96-101, 2015.

%49
\bibitem{BeyerW15}
Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.

%50
\bibitem{RochaIFM12}
Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.
